Comparative Analysis of the wav2vec 2.0 Feature Extractor

### 2023-03-05 main.tex
comment on improved GT baseline
nitpicking

\subsection{Connectionist Temporal Classification}
We use a \gls{CTC} model for our experiments.
It follows the setup described for the \gls{CTC} model in \cite{zhou2022efficient}.
\TODO{Cite Wei's paper and add more description of the CTC model.}
All models are trained in a purely supervised fashion unless explicitly stated otherwise.
\TODO{Do we use an LM?}

@@

\section{Results}
The results, namely the \glspl{WER} on the LibriSpeech \textit{dev} and \textit{test} sets, for the different \fes are shown in \refTab{table:features_general}.
We can observe that all are within a close range.
The \gls{SC} features slightly outperform the Gammatone baseline, while log Mel features are again marginally better and the \wvtwo \fe yields the best results.
This demonstrates that learnable neural \fes are competitive with hand-designed methods in a purely supervised setup with 960h of training data.
However, a clear advantage of these techniques cannot be deduced from the experimental results.
\input{tables/features_general}

@@

The well known distribution of the Gammatone filters is given in \refFig{fig:first_layer}(a).
\refFig{fig:first_layer}(b) shows the frequency response of the learned \gls{SC} filters.
In line with \cite{tuske2018:waveform}, bandpass filters with a non-linear distribution of center frequencies are learned.
The distribution resembles the Gammatone filterbank and with higher center frequencies, the pass band is also wider.
However, the stopband attenuation is clearly weaker.

The distribution for the \wvtwo \fe's first layer in \refFig{fig:first_layer}(c) does not entail this degree of resemblance.
Again, bandpass filters are learned, however, they have a wider passband, their center frequencies are distributed rather linearly and the stopband attenuation is weak.
Interestingly, the frequency response of the pre-trained \wvtwo \fe in \refFig{fig:first_layer}(d) is very similar to \refFig{fig:first_layer}(c).
This indicates that the properties learned in unsupervised pre-training and supervised \gls{CTC} training are similar.
\input{figures/first_layer}

>>>>

\subsection{Connectionist Temporal Classification}
We use a \gls{CTC} model for our experiments.
It follows the setup described for the \gls{CTC} model in \cite{zhou2022efficient}.
\TODO{Cite Wei's paper and add more description of the CTC model.}
All models are trained in a purely supervised fashion using the \gls{CTC} objective unless explicitly stated otherwise.
A 4-gram \gls{LM} is used and integrated using shallow fusion \cite{gulcehre2015shallow} during decoding.
\TODO{Check LM usage.}

@@

\section{Results}
The results, namely the \glspl{WER} on the LibriSpeech \textit{dev} and \textit{test} sets, for the different \fes are shown in \refTab{table:features_general}.
The baseline performance using Gammatone features is improved compared to \cite{zhou2022efficient} by disabling gradient noise and re-tuning the peak learning rate.
We can observe that all \fes are within a close range.
The \gls{SC} features slightly outperform the Gammatone baseline, while log Mel features are again marginally better and the \wvtwo \fe yields the best results.
This demonstrates that learnable neural \fes are competitive with hand-designed methods in a purely supervised setup with 960h of training data.
However, a clear advantage of these techniques cannot be deduced from the experimental results.
\input{tables/features_general}

@@

The well known distribution of the Gammatone filters is given in \refFig{fig:first_layer}\,(a).
\refFig{fig:first_layer}\,(b) shows the frequency response of the learned \gls{SC} filters.
In line with \cite{tuske2018:waveform}, bandpass filters with a non-linear distribution of center frequencies are learned.
The distribution resembles the Gammatone filterbank and with higher center frequencies, the pass band is also wider.
However, the stopband attenuation is clearly weaker.

The distribution for the \wvtwo \fe's first layer in \refFig{fig:first_layer}\,(c) does not entail this degree of resemblance.
Again, bandpass filters are learned, however, they have a wider passband, their center frequencies are distributed rather linearly and the stopband attenuation is weak.
Interestingly, the frequency response of the pre-trained \wvtwo \fe in \refFig{fig:first_layer}\,(d) is very similar to \refFig{fig:first_layer}\,(c).
This indicates that the properties learned in unsupervised pre-training and supervised \gls{CTC} training are similar.
\input{figures/first_layer}
